Colonies - Compute Continuums across Platforms

### 2023-03-28 paper_2023/paper.tex
wip

\begin{abstract}
This paper presents a novel framework for building 
\end{abstract}

@@

\section{Introduction}
TODO
\section{The Colonies framework}
\label{sec:headings}

>>>>

\begin{abstract}
Running AI/ML models in production is becoming more widespread, and maintaining these systems is more complex

    This paper presents a novel framework for managing computational workload across heterogeneous platforms. Colonies is based on  
a loosly coupled microservice architecture where complex workflows are broken down in composable functions that are executed by independently deployable executors. Using a HTTP protocol, workflows can be expressed declarative in any computer language and be executed across platforms by so-called executors, independently deployed in the cloud, edge, devices, or even in web browser creating compute continuums across platforms. Colonies supports both real-time processing and batch jobs while at the same time offer full tracability and zero-trust security.

The paper

\end{abstract}

@@

\section{Introduction}
TODO
https://modelserving.com/blog/why-do-people-say-its-so-hard-to-deploy-a-ml-model-to-production
\section{The Colonies framework}
\label{sec:headings}
